Guilt, shame, and anti-war action in an authoritarian country at war

### 2023-04-28 manuscript.Rmd
Minor tweak to allow output in word format

---
title: "Guilt, shame, and anti-war action in an authoritarian country at war"
output:
  bookdown::pdf_document2:
    latex_engine: lualatex
    keep_tex: yes
    toc: false
  html_document:
    df_print: paged
  pdf_document: default
header-includes:
  - \usepackage{indentfirst}
  - \usepackage{sectsty}
  - \allsectionsfont{\centering}
  - \usepackage{fontspec}
  - \usepackage{polyglossia}
  - \setdefaultlanguage{english}
  - \setotherlanguages{russian}
  - \setmainfont{Times New Roman}
  - \newfontfamily{\cyrillicfonttt}{Times New Roman} 
  - \usepackage{float} 
  - \usepackage{float} \floatplacement{figure}{H} 
  - \newcommand{\beginsupplement}{\setcounter{table}{0}    
  - \renewcommand{\thetable}{S\arabic{table}} 
  - \setcounter{figure}{0} 
  - \renewcommand{\thefigure}{S\arabic{figure}}}  
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
indent: true
bibliography: references.bib
csl: elife.csl
---

>>>>

---
title: "Guilt, shame, and anti-war action in an authoritarian country at war"
output:
  bookdown::pdf_document2:
    latex_engine: lualatex
    keep_tex: yes
    toc: false
  html_document:
    df_print: paged
  bookdown::word_document2:
    toc: false
always_allow_html: true
header-includes:
  - \usepackage{indentfirst}
  - \usepackage{sectsty}
  - \allsectionsfont{\centering}
  - \usepackage{fontspec}
  - \usepackage{polyglossia}
  - \setdefaultlanguage{english}
  - \setotherlanguages{russian}
  - \setmainfont{Times New Roman}
  - \newfontfamily{\cyrillicfonttt}{Times New Roman} 
  - \usepackage{float} 
  - \usepackage{float} \floatplacement{figure}{H} 
  - \newcommand{\beginsupplement}{\setcounter{table}{0}    
  - \renewcommand{\thetable}{S\arabic{table}} 
  - \setcounter{figure}{0} 
  - \renewcommand{\thefigure}{S\arabic{figure}}}  
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
indent: true
bibliography: references.bib
csl: elife.csl
---
